---
title: "Fig2_Step3_ClusteredPlot_and_HMM"
author: "Andrew Erickson"
output: md_document
---

# Setup

```{r, messages=FALSE}
library(tidyverse)
library(infercnv)
library(Seurat)
library(hdf5r)
library(SpatialInferCNV)
```

# Pre-processing clustered data

Since we have already previously created the count matrices, we just need to re-label the annotations to match the clone annotations in step 2, output an updated annotation file, and then use said file as input (with the original count matrix from step 2) to generate the final runs

```{r, eval = FALSE}
PurestBenigns_All <- read.csv("./Mendeley/ProcessedFilesForFigures/Figure2/Step1/Inputs/Consensus_PurestBenigns_18112020.csv")
PurestBenigns_All$Histology <- "Purest Benigns"

CorrectedBenigns_Consensus_AllCancer_ManualNodes_selected <- read.csv("./Mendeley/ProcessedFilesForFigures/Figure2/Step3/Inputs/Fig2_forclustering.csv")
names(CorrectedBenigns_Consensus_AllCancer_ManualNodes_selected)[2] <- "Histology"

Fig2a_ManualClusters <- rbind(CorrectedBenigns_Consensus_AllCancer_ManualNodes_selected, PurestBenigns_All)

write.table(Fig2a_ManualClusters, "Fig2_ManualClusters_for_ClusteredPlot_and_HMM.tsv", 
            sep = "\t",
            quote = FALSE, 
            col.names = FALSE, 
            row.names = FALSE)
```

# Creating the inferCNV object (prior to run)

```{r, eval = FALSE}
AllCancer_clustered <- infercnv::CreateInfercnvObject(raw_counts_matrix="./Organscale_Unsupervised_Consensus_AllCancer_Counts.tsv", 
                                               gene_order_file="./siCNV_GeneOrderFile.tsv",
                                               annotations_file="./Fig2_ManualClusters_for_ClusteredPlot_and_HMM.tsv",
                                               delim="\t",
                                               ref_group_names="Purest Benigns",
								                               chr_exclude = c("chrM"))
```

# Unsupervised Run - (Typically ran on cluster)

```{r, eval = FALSE}
AllCancer_clustered = infercnv::run(AllCancer_clustered,
                                              cutoff=0.1,
                                              out_dir="./Figure2_Step3/Outputs", 
					                                    num_threads = 20,
                                              cluster_by_groups=TRUE, 
                                              denoise=TRUE,
                                              HMM=TRUE)
```



