---
title: "Figure2_Step1_unsupervised_allcancer"
author: "Andrew Erickson"
output: md_document
---
#Setup

```{r setup, messages=FALSE}
library(tidyverse)
library(SpatialInferCNV)
```

#Creating a working directory

We start by creating an empty working directory so that all downloaded files are organized in one place. Something like:

```{r, eval = FALSE}
dir.create("Figure2_output")
setwd("Figure2_output")
```

# Consensus Purest Benigns

```{r, eval = FALSE}
PurestBenigns_All <- read.csv("./Mendeley/ProcessedFilesForFigures/Figure2/Step1/Consensus_PurestBenigns.csv")
```

# Re-creating All Cancer Annotations

```{r, eval = FALSE}
H1_2_Annotations <- ImportHistologicalAnnotations("H1_2", "./Mendeley/Patient 1/Visium/H1_2/H1_2_Final_Consensus_Annotations.csv")
H1_2_CancerSpots <- filter(H1_2_Annotations, Histology == "GG1")

H1_4_Annotations <- ImportHistologicalAnnotations("H1_4", "./Mendeley/Patient 1/Visium/H1_4/H1_4_Final_Consensus_Annotations.csv")
H1_4_CancerSpots <- filter(H1_4_Annotations, Histology == "GG2" | Histology ==  "GG4 Cribriform")

H1_5_Annotations <- ImportHistologicalAnnotations("H1_5", "./Mendeley/Patient 1/Visium/H1_5/H1_5_Final_Consensus_Annotations.csv")
H1_5_CancerSpots <- filter(H1_5_Annotations, Histology ==  "GG4 Cribriform")

H2_1_Annotations <- ImportHistologicalAnnotations("H2_1", "./Mendeley/Patient 1/Visium/H2_1/H2_1_Final_Consensus_Annotations.csv")
H2_1_CancerSpots <- filter(H2_1_Annotations, Histology == "GG2" | Histology ==  "GG4")

H2_2_Annotations <- ImportHistologicalAnnotations("H2_2", "./Mendeley/Patient 1/Visium/H2_2/H2_2_Final_Consensus_Annotations.csv")
H2_2_CancerSpots <- filter(H2_2_Annotations, Histology == "GG2")

H2_5_Annotations <- ImportHistologicalAnnotations("H2_5", "./Mendeley/Patient 1/Visium/H2_5/H2_5_Final_Consensus_Annotations.csv")
H2_5_CancerSpots <- filter(H2_5_Annotations, Histology == "GG4 Cribriform" | Histology == "Transition_State")

rm(H1_2_Annotations,
   H1_4_Annotations,
   H1_5_Annotations,
   H2_1_Annotations,
   H2_2_Annotations,
   H2_5_Annotations)

AllCancers <- rbind(H1_2_CancerSpots, H1_4_CancerSpots)
AllCancers <- rbind(AllCancers, H1_5_CancerSpots)
AllCancers <- rbind(AllCancers, H2_1_CancerSpots)
AllCancers <- rbind(AllCancers, H2_2_CancerSpots)
AllCancers <- rbind(AllCancers, H2_5_CancerSpots)

names(AllCancers)[2] <- "Histology"

rm(H1_2_CancerSpots,
   H1_4_CancerSpots,
   H1_5_CancerSpots,
   H2_1_CancerSpots,
   H2_2_CancerSpots,
   H2_5_CancerSpots)

MergedAll <- rbind(PurestBenigns_All, AllCancers)

rm(PurestBenigns_All)
rm(AllCancers)
```

# Merging Cancer and Benign annotations with the ENSMBLIDs

```{r, eval = FALSE}
H2_1_ENSBMLID_Counts <- ImportCountData("H2_1", "./Mendeley/Patient 1/Visium/H2_1/filtered_feature_bc_matrix.h5")
H2_1_Joined_Counts <- MergingCountAndAnnotationData("H2_1",MergedAll, H2_1_ENSBMLID_Counts)
rm(H2_1_ENSBMLID_Counts)
Counts_joined <- H2_1_Joined_Counts
rm(H2_1_Joined_Counts)

H1_5_ENSBMLID_Counts <- ImportCountData("H1_5", "./Mendeley/Patient 1/Visium/H1_5/filtered_feature_bc_matrix.h5")
H1_5_Joined_Counts <- MergingCountAndAnnotationData("H1_5",MergedAll, H1_5_ENSBMLID_Counts)
rm(H1_5_ENSBMLID_Counts)
Counts_joined <- Counts_joined %>% full_join(H1_5_Joined_Counts, by = "Genes")
rm(H1_5_Joined_Counts)

H2_2_ENSBMLID_Counts <- ImportCountData("H2_2", "./Mendeley/Patient 1/Visium/H2_2/filtered_feature_bc_matrix.h5")
H2_2_Joined_Counts <- MergingCountAndAnnotationData("H2_2",MergedAll, H2_2_ENSBMLID_Counts)
rm(H2_2_ENSBMLID_Counts)
Counts_joined <- Counts_joined %>% full_join(H2_2_Joined_Counts, by = "Genes")
rm(H2_2_Joined_Counts)

H1_2_ENSBMLID_Counts <- ImportCountData("H1_2", "./Mendeley/Patient 1/Visium/H1_2/filtered_feature_bc_matrix.h5")
H1_2_Joined_Counts <- MergingCountAndAnnotationData("H1_2",MergedAll, H1_2_ENSBMLID_Counts)
rm(H1_2_ENSBMLID_Counts)
Counts_joined <- Counts_joined %>% full_join(H1_2_Joined_Counts, by = "Genes")
rm(H1_2_Joined_Counts)

H2_5_ENSBMLID_Counts <- ImportCountData("H2_5", "./Mendeley/Patient 1/Visium/H2_5/filtered_feature_bc_matrix.h5")
H2_5_Joined_Counts <- MergingCountAndAnnotationData("H2_5",MergedAll, H2_5_ENSBMLID_Counts)
rm(H2_5_ENSBMLID_Counts)
Counts_joined <- Counts_joined %>% full_join(H2_5_Joined_Counts, by = "Genes")
rm(H2_5_Joined_Counts)

H1_4_ENSBMLID_Counts <- ImportCountData("H1_4", "./Mendeley/Patient 1/Visium/H1_4/filtered_feature_bc_matrix.h5")
H1_4_Joined_Counts <- MergingCountAndAnnotationData("H1_4",MergedAll, H1_4_ENSBMLID_Counts)
rm(H1_4_ENSBMLID_Counts)
Counts_joined <- Counts_joined %>% full_join(H1_4_Joined_Counts, by = "Genes")
rm(H1_4_Joined_Counts)

V1_2_ENSBMLID_Counts <- ImportCountData("V1_2", "./Mendeley/Patient 1/Visium/V1_2/filtered_feature_bc_matrix.h5")
V1_2_Joined_Counts <- MergingCountAndAnnotationData("V1_2",MergedAll, V1_2_ENSBMLID_Counts)
rm(V1_2_ENSBMLID_Counts)
Counts_joined <- Counts_joined %>% full_join(V1_2_Joined_Counts, by = "Genes")
rm(V1_2_Joined_Counts)

```

# Joining all Counts

```{r, eval = FALSE}
Counts_joined <- Counts_joined %>% replace(., is.na(.), 0)
Counts_joined <- Counts_joined %>% column_to_rownames(., var = "Genes")

write.table(Counts_joined, "Organscale_Unsupervised_Consensus_AllCancer_Counts.tsv", sep = "\t")

MergedAll_Final <- FinalAnnotations(MergedAll, Counts_joined)

write.table(MergedAll_Final, "Organscale_Unsupervised_Consensus_AllCancer_Annotations.tsv", 
            sep = "\t",
            quote = FALSE, 
            col.names = FALSE, 
            row.names = FALSE)
```

# Creating the inferCNV object (prior to run)

```{r, eval = FALSE}
AllCancer_Unsupervised <- infercnv::CreateInfercnvObject(raw_counts_matrix="./Organscale_Unsupervised_Consensus_AllCancer_Counts.tsv", 
                                               gene_order_file="./siCNV_GeneOrderFile.tsv",
                                               annotations_file="./Organscale_Unsupervised_Consensus_AllCancer_Annotations.tsv",
                                               delim="\t",
                                               ref_group_names="Purest Benigns",
								                               chr_exclude = c("chrM"))

```

# Unsupervised Run - (Typically ran on cluster)

```{r, eval = FALSE}
AllCancer_Unsupervised = infercnv::run(AllCancer_Unsupervised,
                                              cutoff=0.1,
                                              out_dir="./Figure2_Step1/Outputs", 
                                              cluster_by_groups=FALSE,
                                              num_threads = 20, 
                                              denoise=TRUE,
                                              HMM=FALSE)
```
